{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
wrote more of the ux sprint appendix

\subsection{Usable Security and User Behavior} %%%
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

{\color {red}  I guess that other literature on general usability applies here too. %so search for it. 
Especially look into browser configuration work. }

@@

\section{UX sprint} 
\label{sec:pilot}
 {\color {red}Details. Gory gory details of how it all went down. 
Include the recruitment process, the setup, what the exact 
tasks were for participants, demographics, everything. 
It all should have a home here.}

%It is easy to overestimate user comprehension and therefore be 
%misguided for user behavior. During this process, we discovered why 
%previous studies had not concentrated on a specific user 
%demographic or focus on advanced features. 
%Even though people download and install on a frequent basis, 
%they do not know how to do it securely and are habituated into doing it in the 
%insecure manner. Of course, this is because the average user's objective is not security. 
%For instance, most of our participants thought the download source was a legitimate site because
%of the look and feel of the site and none our our participants thought to verify the download, 
%even though there were clear instructions to do so on the download page.

\subsection{Motivation}
{\color {red} Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were. }

@@

\subsection{Methodology}
{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.}

\subsection{Results}
{\color {red} Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make. }

@@

\indent \indent  Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

\noindent We transcribed the audio files from our participants' cognitive walkthroughs
and synced them to the screen capture we took during the duration of the experiment:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

>>>>

\subsection{Usable Security and User Behavior} %%%%%%
\indent \indent {\color {red}  Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.}

{\color {red}  I guess that other literature on general usability applies here too.
Especially look into browser configuration work. }

@@

\section{UX sprint} %%%%%%
\label{sec:pilot}
 {\color {red}  Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were. }

@@

\subsection{Methodology} %%%%%%%%%
We 
{\color {red} How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.}

\subsection{Results}
\indent \indent Because of the limited size of the study, it's not possible to state with confidence what 
fraction of users will encounter major usability obstacles. However, it was effective at discovering 
and demonstrating issues that are likely to cause problems for many users. For specific problems 
encountered by an individual user, we refer you to our resources below.

@@

\indent \indent  Online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

\noindent If you would like to observe individual participants' cognitive walkthroughs, 
we transcribed the audio files from our experiment
and synced them to the screen capture we took during the duration of the experiment:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

\subsection{Acknowledgements}
\indent \indent We thank the Tor Project for supporting the sprint, the participants, those who helped us recruit on short notice, and those who helped us plan and set goals and everyone who attended as a developer or observer: Arlo, Arthur, Ashkan, Griffin, Isis, Krishna, Mike, and Nima. We also thank the Tor help desk, whose \#tbb-helpdesk-frequent tag helped us prioritize tickets. Special thanks go to Nima for setting up the collaboration.
